---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# metaboData

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/aberHRML/metaboData/workflows/R-CMD-check/badge.svg)](https://github.com/aberHRML/metaboData/actions)
[![Coverage status](https://codecov.io/gh/aberHRML/metaboData/branch/master/graph/badge.svg)](https://codecov.io/github/aberHRML/metaboData?branch=master)
![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)
<!-- badges: end -->

An R package containing example data sets for metabolomics analyses.

To install directly from this repository run:

```{r,eval=FALSE)
devtools::install_github('aberHRML/metaboData',build_vignettes = TRUE)
```

Or package can be installed via a drat repository hosted on github using:

```{rm,eval=FALSE}
install.packages('metaboData',repos = 'https://aberhrml.github.io/drat/')
```

Available data sets can be viewed using:

```{r}
library(metaboData)

availableDataSets()
```

Available metabolomic techniques can be returned using:

```{r}
techniques()
```

Available data sets for a given metabolomic technique can be returned using:

```{r}
dataSets(techniques()[1])
```

File paths for data files within a given data set can be returned using:

```{r}
files <- filePaths(
    techniques()[1],
    dataSets(techniques()[1])[1])

length(files)
```

An experimental description can be retrieved for a given experiment of a given metabolomic technique using:

```{r}
experimentDescription <- description(
   techniques()[1],
   dataSets(techniques()[1])[1])

str(experimentDescription)
```

Run information can be retrieved for a given experiment of a given metabolomic technique using:

```{r}
info <- runinfo(
    techniques()[1],
    dataSets(techniques()[1])[1])

head(info)
```

The `abr1` FIE-MS data set is included from the [FIEmspro](https://github.com/aberHRML/FIEmspro) package. 