---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# metaboData

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active)
[![Travis build status](https://travis-ci.org/aberHRML/metaboData.svg?branch=master)](https://travis-ci.org/aberHRML/metaboData)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/aberHRML/metaboData?branch=master&svg=true)](https://ci.appveyor.com/project/aberHRML/metaboData)
[![Coverage status](https://codecov.io/gh/aberHRML/metaboData/branch/master/graph/badge.svg)](https://codecov.io/github/aberHRML/metaboData?branch=master)
![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)

An R package containing example data sets for metabolomics analyses.

To install directly from this repository run:

```{r,eval=FALSE)
remotes::install_github('aberHRML/metaboData',build_opts =c("--no-resave-data", "--no-manual"))
```

Or package can be installed via a drat repository hosted on github using:

```{rm,eval=FALSE}
install.packages('metaboData',repos = 'https://aberhrml.github.io/drat/')
```

Available data sets can be viewed using:

```{r}
library(metaboData)

availableDataSets()
```

Available metabolomic techniques can be returned using:

```{r}
techniques()
```

Available data sets for a given metabolomic technique can be returned using:

```{r}
dataSets(techniques()[1])
```

File paths for data files within a given data set can be returned using:

```{r}
files <- filePaths(
    techniques()[1],
    dataSets(techniques()[1])[1])

length(files)
```

An experimental description can be retrieved for a given experiment of a given metabolomic technique using:

```{r}
experimentDescription <- description(
   techniques()[1],
   dataSets(techniques()[1])[1])

str(experimentDescription)
```

Run information can be retrieved for a given experiment of a given metabolomic technique using:

```{r}
info <- runinfo(
    techniques()[1],
    dataSets(techniques()[1])[1])

head(info)
```

The `abr1` FIE-MS data set is included from the [FIEmspro](https://github.com/aberHRML/FIEmspro) package. 