---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# metaboData

[![Travis build status](https://travis-ci.org/aberHRML/metaboData.svg?branch=master)](https://travis-ci.org/aberHRML/metaboData)
[![Coverage status](https://codecov.io/gh/aberHRML/metaboData/branch/master/graph/badge.svg)](https://codecov.io/github/aberHRML/metaboData?branch=master)

An R package containing example data sets for metabolomics analyses

To install this repository run:

```{r,eval=FALSE)
remotes::install_github('aberHRML/metaboData')
```

Available data sets can be viewed using:

```{r}
library(metaboData)

availableDataSets()
```

Available metabolomic techniques can be returned using:

```{r}
techniques()
```

Available data sets for a given metabolomic technique can be returned using:

```{r}
dataSets(techniques()[1])
```

File paths for files within a given data set can be returned using:

```{r}
files <- filePaths(
    techniques()[1],
    dataSets(techniques()[1])[1])

length(files)
```

The `abr1` FIE-MS data set is included from the [FIEmspro](https://github.com/aberHRML/FIEmspro) package. 