---
title: "Using metaboData"
author: "Jasen Finch"
date: "`r Sys.Date()`"
output: 
    prettydoc::html_pretty:
        toc: true
        highlight: github
        theme: tactile
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

metaboData provides raw and processed example metabolomics data sets.
This document concisely outlines how to access the data sets and the meta information provided. 

## Installation using aberhrml *drat* repository

The package can be installed within R directly from a drat repository hosted via github using:

```{r,eval=FALSE}
install.packages('metaboData',repos = 'https://aberhrml.github.io/drat/')
```

## Accessing data sets

Available data sets can be viewed using:

```{r}
library(metaboData)

availableDataSets()
```

Available metabolomic techniques can be returned using:

```{r}
techniques()
```

Available data sets for a given metabolomic technique can be returned using:

```{r}
dataSets(techniques()[1])
```

File paths for data files within a given data set can be returned using:

```{r}
files <- filePaths(
    techniques()[1],
    dataSets(techniques()[1])[1])

length(files)
```

An experimental description can be retrieved for a given experiment of a given metabolomic technique using:

```{r}
experimentDescription <- description(
   techniques()[1],
   dataSets(techniques()[1])[1])

str(experimentDescription)
```

Run information can be retrieved for a given experiment of a given metabolomic technique using:

```{r}
info <- runinfo(
    techniques()[1],
    dataSets(techniques()[1])[1])

head(info)
```

The `abr1` FIE-MS data set is included from the [FIEmspro](https://github.com/aberHRML/FIEmspro) package. 